Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-28 manuscript/manuscript.tex
cleaned up compete figure naming in manuscript

\begin{figure}
\centerline{\includegraphics[width=0.75\textwidth]{figures/compete_3}}
\caption{\label{fig:compete}
\textbf{The congruency between natural selection and the deep mutational scanning measurements decreases with sequence divergence.} 
We fit an ExpCM informed by the H1 or H3 deep mutational scanning experiments to trees spanning sequences with low, intermediate, and high divergence from the sequence used in the experiment. 
The ExpCM stringency parameter ($\beta$) is a measure of the congruency between natural selection and the experimental measurements. 
Larger values of $\beta$ indicate that natural selection prefers the same amino acids as the experiments but with greater stringency. 
As divergence increases between the HA used in the experiment and the other sequences in the tree, the $\beta$ value decreases.
Therefore, the preferences measured in each experiment are progressively less congruent with those of the HA sequences on the tree as we include increasingly diverged sequences. 
\jdbcomment{\emph{Maybe} if logo stacks a bit higher, the point is a bit clearer.}
}
\end{figure}

@@

\begin{suppfig}[H]
\centerline{\includegraphics[width=0.85\textwidth]{figures/lee_compete}}
\caption{\label{supp:lee_compete}
\textbf{The ExpCM defined by H1 preferences lengthen longer branches on the HA tree.} 
\textbf{(A)} An HA alignment was subsampled to create three smaller alignments with varying degrees of divergence from the focal H3 sequence, referred to as "low", "intermediate", and "high". 
\textbf{(B)} The phylogenetic tree of the "high" alignment. 
The colors denote the alignment and the black circle denotes the focal H3 sequence. 
\textbf{(C)} The value of the ExpCM and ExpCM+$\Gamma\omega$ stringency parameter $\beta$ decreases as the divergence from the focal H3 sequence increases. 
\textbf{(D)} Comparisons of branch lengths optimized by the four substitution models for the varying degrees of divergence. 
Black points represent branches from the focal H3 sequence and grey points represent all other branches.  
The branch lengths are in average number of codon substitutions per site. 
}
\end{suppfig}

\begin{suppfig}[H]
\centerline{\includegraphics[width=0.85\textwidth]{figures/compete_4}}
\caption{\label{supp:compete_4}
}
\end{suppfig}

>>>>

\begin{figure}
\centerline{\includegraphics[width=0.75\textwidth]{figures/compete}}
\caption{\label{fig:compete}
\textbf{The congruency between natural selection and the deep mutational scanning measurements decreases with sequence divergence.} 
We fit an ExpCM informed by the H1 or H3 deep mutational scanning experiments to trees spanning sequences with low, intermediate, and high divergence from the sequence used in the experiment. 
The ExpCM stringency parameter ($\beta$) is a measure of the congruency between natural selection and the experimental measurements. 
Larger values of $\beta$ indicate that natural selection prefers the same amino acids as the experiments but with greater stringency. 
As divergence increases between the HA used in the experiment and the other sequences in the tree, the $\beta$ value decreases.
Therefore, the preferences measured in each experiment are progressively less congruent with those of the HA sequences on the tree as we include increasingly diverged sequences. 
\jdbcomment{\emph{Maybe} if logo stacks a bit higher, the point is a bit clearer.}
}
\end{figure}

@@
